---
title: "Characterizing Moissanite Customers"
output: html_document
---

#### Quick look at Moissanite Customers
20869 of people who buy Moissanite at all, buy 33% or less. The other 2117 people buy 34% or more moissanite. These could be our "moissanite" customers. Hardcore customers as well as customers who have 3 or fewer orders have been eliminated.   
```{r setup, echo=FALSE}
require(gridExtra)
require(ggplot2)
require(kohonen)

setwd("~/JewelyMkngCusts/")
jmc <- read.csv("jwlmkngcusts.csv",header=T,sep=',')

jmc <- subset(jmc,TTL_CARTS < 40 & TTL_ORDERS > 3)
moiscust <- subset(jmc, PCT_DIAMOND_SYNTHETIC > 0)
othercusts <- subset(jmc, PCT_DIAMOND_SYNTHETIC ==0)

moiscust$decile <- with(moiscust, cut(PCT_DIAMOND_SYNTHETIC, 
                                breaks=quantile(PCT_DIAMOND_SYNTHETIC, probs=seq(0,1, by=0.1), na.rm=TRUE), 
                                include.lowest=TRUE))

g1 <- ggplot(moiscust, aes(decile)) + geom_bar() + ggtitle("Customers (by deciles) who purchased Moissanite ")
g2 <- t(data.frame(table(moiscust$decile)))
mytheme <- gridExtra::ttheme_default(
    core = list(fg_params=list(cex = 2.0)),
    colhead = list(fg_params=list(cex = 1.0)),
    rowhead = list(fg_params=list(cex = 1.0)))

g2 <- tableGrob(g2,theme=mytheme)

grid.arrange(g1,g2, heights=c(3,1))

ggplot(moiscust, aes(PCT_DIAMOND_SYNTHETIC)) +geom_histogram(bins=100) +geom_vline(xintercept=0.33) + annotate('text',label="20869 (out of 22986, 90%)\n customers buy 33% or less of Moissanite", x=0.5, y = 1000) + ggtitle("Distirbution of Customers who Purchase Moissanite")
```

#### Let's see if these customers group together during SOM
First I cap off variables at 0.01 and 0.98 to get rid of extreme outliers. The data is then scaled and coverted to a matrix for the process.

Variables used in the algorithm | RFMs were not used 
--------------------------------|---------------------------
TTL_GPS                         | TTL_NET_REV
TTL_GM                          | TTL_ORDERS
TTL_CARTS                       | TTL_QTY
PCT_ORDERS_DISC                 | TTL_DISC_AMT
PCT_JWL                         | PCT_GEM
PCT_COLOR_SILVER                | PCT_GEMSTONES_DEPT
PCT_DIAMOND_GOLD                | PCT_DIAMOND_SILVER
PCT_COLOR_GOLD                  | PCT_KITS
PCT_PEARLS                      | PCT_GEM_GIFTS
PCT_BELLA_LUCE                  | PCT_JWL_MAKING
PCT_WATCHES                     | PCT_COLOR_PLATED
PCT_GOLD                        | PCT_COSTUME
PCT_DIAMOND_SYNTHETIC           | PCT_OTHER_DEPT
PCT_BROAD                       | PCT_INET
PCT_OTHER                       | PCT_BROAD_INFL
PCT_SP                          | TTL_RETURN_AMT
TTL_SHIP                        | AVG_ORDER_VAL
AVG_PRICEPT                     | AVG_DAYS_BTW_ORDS
```{r, echo=FALSE}
#function to cap variables at some percentile
capVector <- function(x,probs=c(0.01,0.98)) {
  ranges <- quantile(x, probs=probs, na.rm=T)
  x[x < ranges[1]] <- ranges[1]
  x[x > ranges[2]] <- ranges[2]
  return(x)
}

#variables deleted: DUPL_ID, VC_CLUSTER, LAYER_RANK,RFM_RECENCY,RFM_FREQUENCY,RFM_MONETARY, DAYPART_BIN,TIMERANGE_BIN PCT_DAYPART_BIN, TTL_DISC_ORDERS, TTL_JWL_ORDERS, TTL_GEM_ORDERS, TTL_BROAD_ORDERS, TTL_INET_ORDERS, TTL_OTHER_ORDERS, TTL_BROAD_INFL_ORDERS, TTL_PA_ORDERS, PCT_PA, TTL_SP_ORDERS, LTY_REW_LVL, NEW_CUST, NEW_PA_CUST

moisscustomers <- moiscust[,-c(1:9,16,19,21,39,41,43,45,47:49,51:53,59:61)]
moisscustomers[is.na(moisscustomers)] <- 0

moissnooutliers <- data.frame(matrix(ncol=36,nrow=22986))

for(i in 1:36) {
  moissnooutliers[,i] <- capVector(moisscustomers[,i])
}

colnames(moissnooutliers)[1:36] <- names(moisscustomers)

mois_std <- as.matrix(scale(moissnooutliers))


set.seed(123)
fa_standard.som <- som(mois_std, grid=somgrid(20,20,'hexagonal'),keep.data=T)
par(mfrow=c(1,2))
plot(fa_standard.som,type='changes')
p <- plot(fa_standard.som,type='counts')
```


#### What exactly do the colors on the Moissanite chart mean?
The actual percentages were scaled and those scaled values correspond to "code" values that are then plotted. Note: higher and lower values got forced to 0.01th percentile and 98th percentile. 
```{r,echo=FALSE}
# function to color the plot
coolBlueHotRed <- function(n, alpha = 1) {
rainbow(n, end=4/6, alpha=alpha)[n:1]
}

#contains actual moiss %, scaled moiss %, and the corresponding codes
moissnooutliers <- moissnooutliers[order(moissnooutliers$PCT_DIAMOND_SYNTHETIC),]
moisact <- unique(moissnooutliers$PCT_DIAMOND_SYNTHETIC)

moisscaled <- sort(fa_standard.som$data[,25])
moisscaled <- unique(moisscaled)

moisvalues <- cbind.data.frame(moisact,moisscaled)

par(mfrow=c(2,2))
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,25], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[25]) 

plot(fa_standard.som, type="property",property=fa_standard.som$codes[,1], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[1]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,2], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[2]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,3], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[3]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,4], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[4]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,5], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[5]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,6], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[6]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,7], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[7]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,8], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[8]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,9], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[9]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,10], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[10]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,11], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[11]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,12], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[12]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,13], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[13]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,14], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[14]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,15], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[15]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,16], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[16]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,17], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[17]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,18], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[18]) 


plot(fa_standard.som, type="property",property=fa_standard.som$codes[,19], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[19]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,20], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[20]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,21], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[21]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,22], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[22]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,23], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[23]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,24], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[24]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,26], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[26]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,27], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[27]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,28], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[28]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,29], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[29]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,30], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[30]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,31], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[31]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,32], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[32]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,33], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[33]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,34], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[34]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,35], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[35]) 
plot(fa_standard.som, type="property",property=fa_standard.som$codes[,36], palette.name = coolBlueHotRed, main = colnames(fa_standard.som$data)[36]) 

```


#### How do these results look up against the larger customer base?
```{r}

othercustomers <- othercusts[,-c(1:9,16,19,21,39,41,43,45,47:49,51:53,59:61)]
othercustomers[is.na(othercustomers)] <- 0

othernooutliers <- data.frame(matrix(ncol=36,nrow=259550))


for(i in 1:36) {
  othernooutliers[,i] <- capVector(othercustomers[,i])
}

colnames(othernooutliers)[1:36] <- names(othercustomers)

other_std <- as.matrix(scale(othernooutliers))
other_std <- other_std[,-25]


set.seed(123)
lrgcustbase.som <- som(other_std, grid=somgrid(20,20,'hexagonal'),keep.data=T)
par(mfrow=c(1,2))
plot(lrgcustbase.som,type='changes')
p <- plot(lrgcustbase.som,type='counts')
par(mfrow=c(2,2))


plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,1], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[1]) 
plot(fa_standard.som, type="property",property=lrgcustbase.som$codes[,2], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[2]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,3], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[3]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,4], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[4]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,5], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[5]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,6], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[6]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,7], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[7]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,8], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[8]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,9], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[9]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,10], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[10]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,11], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[11]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,12], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[12]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,13], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[13]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,14], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[14]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,15], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[15]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,16], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[16]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,17], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[17]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,18], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[18]) 


plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,19], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[19]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,20], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[20]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,21], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[21]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,22], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[22]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,23], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[23]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,24], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[24]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,25], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[25]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,26], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[26]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,27], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[27]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,28], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[28]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,29], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[29]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,30], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[30]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,31], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[31]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,32], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[32]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,33], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[33]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,34], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[34]) 
plot(lrgcustbase.som, type="property",property=lrgcustbase.som$codes[,35], palette.name = coolBlueHotRed, main = colnames(lrgcustbase.som$data)[35]) 


```


```{r,echo=FALSE}
#variables deleted: DUPL_ID, VC_CLUSTER, LAYER_RANK,DAYPART_BIN,TIMERANGE_BIN, PCT_DAYPART_BIN, TTL_DISC_ORDERS, TTL_JWL_ORDERS, TTL_GEM_ORDERS, TTL_BROAD_ORDERS, TTL_INET_ORDERS, TTL_OTHER_ORDERS, TTL_BROAD_INFL_ORDERS, TTL_PA_ORDERS, PCT_PA, TTL_SP_ORDERS, LTY_REW_LVL, NEW_CUST, NEW_PA_CUST

moisscustomersRFM <- moiscust[,-c(1:3,7:9,16,19,21,39,41,43,45,47:49,51:53,59:61)]
moisscustomersRFM[is.na(moisscustomersRFM)] <- 0

moissnooutliersRFM <- data.frame(matrix(ncol=39,nrow=22986))

for(i in 1:39) {
  moissnooutliersRFM[,i] <- capVector(moisscustomersRFM[,i])
}

colnames(moissnooutliersRFM)[1:39] <- names(moisscustomersRFM)

mois_stdRFM <- as.matrix(scale(moissnooutliersRFM))




set.seed(123)
fa_standard.somRFM <- som(mois_stdRFM, grid=somgrid(20,20,'hexagonal'),keep.data=T)
par(mfrow=c(1,1))
plot(fa_standard.somRFM,type='changes')
plot(fa_standard.somRFM,type='counts')


# function to color the plot
coolBlueHotRed <- function(n, alpha = 1) {
rainbow(n, end=4/6, alpha=alpha)[n:1]
}

par(mfrow=c(2,2))
plot(fa_standard.somRFM,type='counts')
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,28], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[28]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,1], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[1]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,2], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[2]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,3], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[3]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,4], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[4]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,5], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[5]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,6], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[6]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,7], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[7]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,8], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[8]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,9], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[9]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,10], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[10]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,11], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[11]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,12], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[12]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,13], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[13]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,14], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[14]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,15], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[15]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,16], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[16]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,17], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[17]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,18], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[18]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,19], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[19]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,20], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[20]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,21], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[21]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,22], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[22]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,23], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[23]) 

 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,24], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[24]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,26], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[26]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,27], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[27]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,25], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[25]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,29], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[29]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,30], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[30]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,31], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[31]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,32], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[32]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,33], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[33]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,34], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[34]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,35], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[35]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,36], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[36])
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,37], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[37]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,38], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[38]) 
plot(fa_standard.somRFM, type="property",property=fa_standard.somRFM$codes[,39], palette.name = coolBlueHotRed, main = colnames(fa_standard.somRFM$data)[39]) 


```





